Analysis of split plot design using MCMCglmm

### 2020-05-19 README.Rmd
Fix instructions for cloning
Update link to personal site
Spellcheck and remove extra "/" in a URL

```
git clone https://github.com/adamhsparks/rice_awd_pests.git
```

@@

Once logged in, use the Files pane (bottom right) open the folder for this
project, and open the `.Rproj` file for this project. Once that's open, you'll
see the `analysis/paper` directory in the Files pane where you can find the R
markdown document, and knit them to produce the results in the paper. More
information about using RStudio in Docker is avaiable at the
[Rocker](https://github.com/rocker-org)
[wiki](https://github.com/rocker-org/rocker/wiki/Using-the-RStudio-image) pages.

@@

(+61) 7.4631.1948   adam.sparks@usq.edu.au  
https://staffprofile.usq.edu.au/Profile/Adam-Sparks

>>>>

```
git clone https://github.com/adamhsparks/rice_AWD_ShB_analysis.git
```

@@

Once logged in, use the Files pane (bottom right) open the folder for this
project, and open the `.Rproj` file for this project. Once that's open, you'll
see the `analysis/paper` directory in the Files pane where you can find the R
markdown document, and knit them to produce the results in the paper. More
information about using RStudio in Docker is available at the
[Rocker](https://github.com/rocker-org)
[wiki](https://github.com/rocker-org/rocker/wiki/Using-the-RStudio-image) pages.

@@

(+61) 7.4631.1948   adam.sparks@usq.edu.au  
https://adamhsparks.com/
